A multiverse analysis of the associations between internet use and well-being

### 2023-11-13 ms.Rmd
More reproducibility improvements

# If only simulated data exists, sun small subset of specs
set.seed(9091090)
if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = MAX_CORES)
```

@@

path <- "tmp/specs-lmer-total.rds"
if (!file.exists(path)) {

@@

  saveRDS(specs_avg, path)
} else {specs_avg <- readRDS(path)}

# Median association (with reversed negative experiences)
# tmp <- specs_avg %>% 
#   mutate(estimate = if_else(y == "negative_experiences", -1*estimate, estimate)) %>% 
#   summarise(across(c(estimate, std.error), median))
```

@@

```{r}
#| label: fig-rq1
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 5.6
#| fig.width: 9
#| fig.cap: Scatterplots of countries' mean well-being outcomes for individuals who responded No and Yes to the internet question, and their differences. Small points are countries' means, and solid colored points and lines are means of the countries' means. Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\% confidence interval. The GWBI outcomes did not overlap in time with mobile internet data.

@@

```{r}
#| include: true
#| label: fig-multiverse
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 6
#| fig.width: 9
#| fig.cap: Multiverse analysis results of associations between three internet use predictors and eight well-being outcomes. The estimated associations are ordered by increasing magnitude; the x-axis denotes the ordered number of (predictor * age * sex * covariate combination * weights) specification. The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point. 
draw_sca <- function(mv, Y) {
  this_mv <- filter(mv, y %in% Y) %>% 
    mutate(y = factor(y, levels = Y))
  p1 <- this_mv %>% 
    ggplot(aes(i, estimate, col = decision)) +
    scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
    scale_y_continuous(
      position = "right",
      "Estimated association (95%CI)",
      breaks = extended_breaks(7)
    ) +
    scale_x_continuous(
      "Analysis specification (in order of association magnitude)",
      breaks = extended_breaks(5),
      expand = expansion(.015)
    ) +
    geom_hline(yintercept = 0, linewidth = .1) +
    geom_point(size = .25) +
    geom_linerange(
      aes(ymin = conf.low, ymax = conf.high),
      linewidth = .2, alpha = .2
    ) +
    geom_ysidedensity(
      aes(x = after_stat(ndensity)), 
      col = "grey20", fill = "grey60", alpha = .4, n = 3001
    ) +
    geom_ysidepoint(
      data = this_mv %>% 
        group_by(y) %>% 
        summarise(median = median(estimate)) %>% 
        # Just for coloring the dot
        mutate(
          decision = cut(
            median,
            breaks = c(-1, -.0001, .0001, 1),
            labels = c("Negative", "Not significant", "Positive")
          )
        ),
      aes(y = median, x = 0),
      size = 2, position = position_nudge(x = .025)
    ) +
    scale_ysidex_continuous(expand = expansion(c(0, .2))) +
    facet_wrap(
      "y", 
      scales = "free_x", 
      ncol = 4, 
      drop = TRUE,
      labeller = as_labeller(sanitize_labels)
    ) +
    theme(
      axis.title.x = element_blank(),
      legend.position = "none",
      ggside.panel.scale = 0.1,
      ggside.panel.spacing.x = unit(0, "pt"),
      ggside.axis.text = element_blank(),
      ggside.axis.ticks = element_blank()
    )

>>>>

# If only simulated data exists, run just 1 spec by every X, Y pair
set.seed(9091090)
if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = 1, by = c(y, x))
```

@@

path <- "tmp/multiverse-lmer-average.rds"
if (!file.exists(path)) {

@@

  saveRDS(specs_avg, path)
} else {specs_avg <- readRDS(path)}
```

@@

```{r}
#| label: fig-rq1
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 5.6
#| fig.width: 9
#| fig.cap: "Scatterplots of countries' mean well-being outcomes for individuals who responded No and Yes to the internet question, and their differences. Small points are countries' means, and solid colored points and lines are means of the countries' means. Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\% confidence interval. The GWBI outcomes did not overlap in time with mobile internet data."

@@

```{r}
#| include: true
#| label: fig-multiverse
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 6
#| fig.width: 9
#| fig.cap: "Multiverse analysis results of associations between three internet use predictors and eight well-being outcomes. The estimated associations are ordered by increasing magnitude; the x-axis denotes the ordered number of (predictor * age * sex * covariate combination * weights) specification. The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point. "

draw_sca <- function(mv, Y) {
  this_mv <- filter(mv, y %in% Y) %>% 
    mutate(y = factor(y, levels = Y))
  p1 <- this_mv %>% 
    ggplot(aes(i, estimate, col = decision)) +
    scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
    scale_y_continuous(
      position = "right",
      "Estimated association (95%CI)",
      breaks = extended_breaks(7)
    ) +
    scale_x_continuous(
      "Analysis specification (in order of association magnitude)",
      breaks = extended_breaks(5),
      expand = expansion(.015)
    ) +
    geom_hline(yintercept = 0, linewidth = .1) +
    geom_point(size = .25) +
    geom_linerange(
      aes(ymin = conf.low, ymax = conf.high),
      linewidth = .2, alpha = .2
    ) +
    geom_ysidedensity(
      aes(x = after_stat(ndensity)), 
      col = "grey20", fill = "grey60", alpha = .4, n = 3001
    ) +
    geom_ysidepoint(
      data = this_mv %>% 
        group_by(y) %>% 
        summarise(median = median(estimate)) %>% 
        # Just for coloring the dot
        mutate(
          decision = cut(
            median,
            breaks = c(-1, -.0001, .0001, 1),
            labels = c("Negative", "Not significant", "Positive")
          )
        ),
      aes(y = median, x = 0),
      size = 2, position = position_nudge(x = .025)
    ) +
    scale_ysidex_continuous(expand = expansion(c(0, .2))) +
    facet_wrap(
      "y", 
      scales = "free_x", 
      ncol = 4, 
      drop = TRUE,
      labeller = as_labeller(sanitize_labels)
    ) +
    theme(
      axis.title.x = element_blank(),
      legend.position = "none",
      ggside.panel.scale = 0.1,
      ggside.panel.spacing.x = unit(0, "pt"),
      ggside.axis.text = element_blank(),
      ggside.axis.ticks = element_blank()
    )
